R Notebook

### 2023-01-05 Code/Simulation.Rmd
Testing auto arima for fitted + dependence

```{r Autoarma}
source("autoarma.R")

@@

>>>>

```{r Autoarma D}
source("autoarma.R")

@@

```{r Autoarma FD}
test_autoarma_FD <- function(x, pdist, qdist, B = 1000, working=c("auto", "2,2")) {
    z <- qnorm(pdist(x))

    n <- length(x)
    m <- mean(x)
    v <- var(x)
    scale <- v/m
    shape <- m*m/v

    stat  <- ks.test(x, "pgamma", shape = shape, scale = scale)$statistic

    if (working == "auto") {
        fit <- forecast::auto.arima(z, ic = "aic", max.d = 0, max.D = 0, allowmean = FALSE)
        ## stepwise=FALSE, approximation=FALSE)
        ## working model: p.max = q.max = 5
    } else {
        pq <- as.numeric(unlist(strsplit(working, ",")))
        fit <- arima(z, order = c(pq[1], 0, pq[2]), include.mean = FALSE) ## working arma(2, 2)
    }
    model <- list(ar = fit$model$phi, ma = fit$model$theta)

    ## theoretical variance of arma; note the negative sign of theta; McLeod (1975)
    sigma <- sqrt(ltsa::tacvfARMA(phi = model$ar, theta = - model$ma, maxLag = 0))

    stat.b <- rep(0, B)
    for (i in 1:B) {
        z.b <- arima.sim(model, n = n)
        ##   arma(1, 1) only: sd = sqrt (1 - ophi^2) / (1 + 2 * phi * theta + theta^2))
        x.b <- qgamma(pnorm(z.b, mean = 0, sd = sigma), shape = shape, scale = scale)

        # Calculate new test statistic
        stat.b[i] <- ks.test(x.b, "pgamma", shape = shape.b, scale = scale.b)$statistic
    }
    p.value <- mean(stat.b >= stat)

# Generate results
nrep <- 1000
n <- 200
phi <- .3
theta <- .2
shape <- 3
scale <- 1
qdist <- function(u) qgamma(u, shape = shape, scale = scale)
pdist <- function(u) pgamma(u, shape = shape, scale = scale)
working <- "auto"
counter <- 0

pvals_autoarma <- replicate(nrep, test_autoarma_FD(x = genData(n, phi, theta, qdist), 
                                                   pdist = pdist, 
                                                   qdist = qdist, 
                                                   B = 1000, 
                                                   working = working)$p.value)
counter <- 0

# P-vals from using parametric bootstrap
pvals_parametric <- replicate(nrep, test_parametric_gamma(genData(n, phi, theta, qdist))$p.value)

pvals_naive <- replicate(nrep, test_super_naive_gamma(genData(n, phi, theta, qdist))$p.value)

# Create a master data_frame with all the results
histogram <- c(rep("Autoarma", nrep), rep("Naive Parametric", nrep), rep("Super Naive", nrep))
p_values <- c(pvals_autoarma, pvals_parametric, pvals_naive)
results <- data_frame(p_values, histogram)

results$histogram <- factor(results$histogram, levels = c("Super Naive", "Naive Parametric", "Autoarma"))

# Generate histograms plot
hist_autoarma_FD <- ggplot(results) + 
                   geom_histogram(aes(x = p_values, fill = histogram), boundary = 0, binwidth = 1/20) + 
                   scale_x_continuous(name = "p-value", breaks=c(0, 1)) + 
                   theme(legend.position = "none") +
                   facet_wrap(~histogram, scales = "free_y")
hist_autoarma_FD

# Save the histogram figure
ggsave(filename = "hist_autoarma_FD.pdf", plot = hist_autoarma_FD, path = "../Manuscript", height = 2.1, width = 6)
```
